Grove: A Convergent Collaborative Structure-Editor Calculus

### 2021-07-27 grove-paper-3-formalism.tex
fix well sortedness defs
add source annotation to \conflictHole

The language we are modeling is shown in \autoref{fig:Base syntax}, standard for a simply-typed lambda calculus except that all sorts have empty holes (represented by $\hole$) and conflict holes (of the form $\conflictHole{q,\ldots,q}$).
In particular, the argument of a lambda can be either a bound variable or a hole.
Additionally, all non-hole forms have a superscripted identifier $u \in \U$.

@@

A vertex $v = (u, k)$ identifies a distinct instance of some constructor $k \in
\K$, corresponding to a non-hole form defined in \autoref{fig:Base syntax}. Each
contructor has an arity, which we define as a set of positions. A position $p
\in \P$ identifies a location at some originating vertex from which edges to
destination vertices may originate. The $\arity$ function in
\autoref{fig:Constructors, Indexes and Arity} gives the complete mapping from
constructors to potential edge positions with their corresponding sorts. Every
graph contains a distinguished root vertex, root constructor, and root position,
respectively named $v_0$, $k_0$, and $p_0$.

@@

We define the semantics of graph actions via the following transition relation
between graphs.
\[
  G \overset{(s,\e)}{\longrightarrow} G\left[ \e \mapsto s \sqcup G(\e) \right\}
\]
Applying graph action $\left(s, \e\right)$ to graph $G$ results in the
updated graph $G' = G\left[\e \mapsto s \sqcup G(\e) \right]$, wherein the edge
state associated with edge $\e$ in $G$ becomes the join of $s$ with the state of
$\e$ in $G$, and $G'(\e') = G(\e')$ for all other $\e' \ne \e$ in the domain of
$G$.

>>>>

The language we are modeling is shown in \autoref{fig:Base syntax}, standard for a simply-typed lambda calculus except that all sorts have empty holes (represented by $\hole$) and conflict holes (of the form $\conflictHole{q,\ldots,q}{v}{p}$).
In particular, the argument of a lambda can be either a bound variable or a hole.
Additionally, all non-hole forms have a superscripted identifier $u \in \U$.

@@

A vertex $v = (u, k)$ identifies a distinct instance of some constructor $k \in
\K$, corresponding to a non-hole form defined in \autoref{fig:Base syntax}. Each
contructor has an arity, which we define as a set of positions. A position $p
\in \P$ identifies a location at some originating vertex from which edges to
destination vertices may originate. The $\arityOp$ function in
\autoref{fig:Constructors, Indexes and Arity} gives the complete mapping from
constructors to potential edge positions with their corresponding sorts. Every
graph contains a distinguished root vertex, root constructor, and root position,
respectively named $v_0$, $k_0$, and $p_0$.

@@

We define the semantics of graph actions via the following transition relation
between graphs.
\[
  G \overset{(s,\e)}{\longrightarrow} G\left[ \e \mapsto s \sqcup G(\e) \right]
\]
Applying graph action $\left(s, \e\right)$ to graph $G$ results in the
updated graph $G' = G\left[\e \mapsto s \sqcup G(\e) \right]$, wherein the edge
state associated with edge $\e$ in $G$ becomes the join of $s$ with the state of
$\e$ in $G$, and $G'(\e') = G(\e')$ for all other $\e' \ne \e$ in the domain of
$G$.
